SplitHalf_ICC

### 2023-05-14 Step6_SensitivityAnalyses/SplitHalfReliability/splithalf_ICCs.Rmd
Update splithalf_ICCs.Rmd
added comment on line 96

# Save results (the above step takes a while to run)
write.csv(ICC_results,'/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/ICCresults_10subj_17PFNs.csv')
```

>>>>

# Save results (the above step takes a while to run)
write.csv(ICC_results,'/Users/askeller/Documents/Kellernet_PrelimAnalysis/RevisionAnalyses_PFNsCog/SplitHalfReliability/ICCresults_10subj_17PFNs.csv') 
## Note: remove first column of this csv (containing only strings of "ICCs_sub") before loading the results back in below
```
